Methodology for Assessing the State of the Practice for Domain X

### 2020-11-12 StateOfPractice/Methodology/Methodology.tex
updated wording in section 6 methodology

If the list of software is too long (over around 30 packages), then steps need
to be taken to create a more manageable list. To reduce the length of the list,
the following filters are applied in the priority order listed, stopping once
the desired number of projects is reached:

>>>>

If the list of software is too long (over around 30 packages), then steps need
to be taken to create a more manageable list. To reduce the length of the list,
the following filters are applied in the priority order listed, stopping once
a manageable number of projects is reached:
